\Large \bf Cyclone: High Availability for Persistent Key Value Stores

### 2017-08-05 paper/paper.tex
Updates.

Consensus in a box~\cite{consensus_box} implements the Zookeeper atomic
broadcast protocol together with a NIC on an FPGA. That work ignored durability,
focusing purely on network performance for replication. Latency is
excellent due to the FPGA that cuts out the path from CPU caches to the NIC and
are reported to be as low as 3us for a round trip from leader to follower
replica compared to the 6us we observe with DPDK. Notably however they reported
7us when using TCP/IP from the FPGA rather than their own connection oriented
network protocol. On the other hand their peak replication throughput is 6M
replications/sec on 66 Gbps of aggregate network bandwith, comparable to the
same mark obtained by Cyclone on an aggregate 40 Gbps of network bandwidth when
not using the log on the SSD. We believe the general applicability afforded by
our software only solution together with the fact that we provide persistence by
design makes it a compelling alternative to an FPGA based solution even given
the larger latency.

>>>>

Consensus in a box~\cite{consensus_box} implements the Zookeeper atomic
broadcast protocol together with a NIC on an FPGA. That work ignored durability,
focusing purely on network performance for replication. Latency is excellent due
to the FPGA that cuts out the path from CPU caches to the NIC and are reported
to be as low as 3us for a round trip from leader to follower replica compared to
the 6us we observe with DPDK. Notably however they reported 7us when using
TCP/IP from the FPGA rather than their own connection oriented network
protocol. On the other hand their peak replication throughput is 4M
replications/sec on 66 Gbps of aggregate network bandwith for small messages,
comparable to the 6M replications/sec mark obtained by Cyclone on an aggregate
40 Gbps of network bandwidth when \emph{also persisting the log on the SSD}. We
believe the general applicability afforded by our software only solution
together with the fact that we provide persistence by design makes it a
compelling alternative to an FPGA based solution even given the larger latency.
